---
title: "cancerrisk"
author: "Maydelis K. Minaya and Shuai Xie"
date: "12/16/18"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction

With the incidence of cancer at an all-time high, it is imperative to learn about the associated risk factors in order to be better equipped to take proactive measures. According to the United States National Institute of Health (NIH), an estimated 1,735,350 new cases of cancer will be diagnosed in the U.S. each year and 609,640 people will die from the disease in 2018. Given the unsettling implications of this data action is required. We have created a tool for researchers to build cancer prediction models. Our package includes basic functions that are user friendly and highly interactive. These functions will help investigators build cancer prediction models because they take into account numerous variables relevant to cancer models. The cancerrisk package has 5 main functions that users can incorporate into their cancer risk assessment models.

Statistics from: <https://www.cancer.gov/about-cancer/understanding/statistics>


- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
